Distributional Trees and Forests

### 2017-11-30 pkg/disttree/inst/CMStatistics2017/slides_rain.Rnw
started rewrting application slides
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1784 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 7b13f2926dc4e27ba18ac49528154a9ffdae2ac1

\title{Distributional Trees and Forests}
\author{Lisa Schlosser, Torsten Hothorn,\\ Heidi Seibold, Achim Zeileis}
\setbeamerfont{url}{size*={11.5pt}{13pt},series=\mdseries}
\URL{https://R-Forge.R-project.org/projects/partykit/}
\headerimage{3}

@@

\SweaveOpts{engine=R, eps=FALSE, keep.source=TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", useFancyQuotes = FALSE, width = 70)
library("ggplot2")
theme_set(theme_bw(base_size = 18))
library("disttree")
#library("partykitR1")
library("gamlss")
library("lattice")
library("crch")
library("latex2exp")
library("parallel")
library("gamlss.cens")
gen.cens(NO, type = "left")

@@

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\begin{center}
\vspace*{-0.2cm}
<<rain_cross_axams_crps_skills_score, fig=TRUE, echo=FALSE, height=5.2>>=
boxplot(1 - rain_crps[,c(2,3,4)] / rain_crps[,6], ylim = c(-0.005, 0.065),
        main = "Cross Validation (with reference model EMOS)",
        names = c("Forest", "prespecified GAM", "boosted GAM"),
        ylab = "CRPS skills score", col = "lightgray") 
abline(h = 0, col = pal["EMOS"], lwd = 2)
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Application for all stations:
\begin{itemize}
\item Learn forest model on data from 24 years (1985--2008).
\item Evaluate on 4 years (2009--2012).
\item Compare to commonly used methods:\\
\begin{itemize}
\item Prespecified GAM
\item Boosted GAM
\item Ensemble Model Output Statistics (EMOS) 
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\title{Distributional Trees and Forests}
\author{Lisa Schlosser, Torsten Hothorn,\\ Heidi Seibold, Reto Stauffer, Achim Zeileis}
\setbeamerfont{url}{size*={11.5pt}{13pt},series=\mdseries}
\URL{https://R-Forge.R-project.org/projects/partykit/}
\headerimage{3}

@@

\SweaveOpts{engine=R, eps=FALSE, keep.source=TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", useFancyQuotes = FALSE, width = 70)
library("ggplot2")
theme_set(theme_bw(base_size = 18))
library("disttree")
library("Formula")
#library("partykitR1")
library("gamlss")
library("lattice")
library("crch")
library("latex2exp")
library("parallel")
library("gamlss.cens")
gen.cens(NO, type = "left")

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Task:
\begin{itemize}
\item Goal: Predict total precipitation amount.
\item Input: Numerical Weather Prediction (NWP) with gridsize ... .
\item 
\vspace{0.1cm}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\begin{center}
\vspace*{-0.2cm}
<<rain_cross_axams_crps_skills_score, fig=TRUE, echo=FALSE, height=5.2>>=
boxplot(1 - rain_crps[,c(2,3,4)] / rain_crps[,6], ylim = c(-0.005, 0.065),
        main = "Cross validation (with reference model EMOS)",
        names = c("Forest", "prespecified GAM", "boosted GAM"),
        ylab = "CRPS skills score", col = "lightgray") 
abline(h = 0, col = pal["EMOS"], lwd = 2)
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Application for all 95 stations:
\begin{itemize}
\item Learn forest model on data from 24 years (1985--2008).
\item Evaluate on 4 years (2009--2012).
\item Compare to commonly used methods:\\
\begin{itemize}
\item Prespecified GAM
\item Boosted GAM
\item Ensemble Model Output Statistics (EMOS) 
\end{itemize}
\end{itemize}
\end{frame}
